Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-07-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
add bio and pictures

% The photo area is 1 in wide and 1.25 in long. The IEEE recommends that author photo images should be of 220 dpi (dots per inch) resolution and in gray scale with 8 bits/sample.
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./jpg/pschratz.jpeg}}]{Patrick Schratz}
%	[]{Patrick Schratz}
	is a Data Scientist currently working in Zurich, CH.
    His area of expertise is applied machine learning, more specifically the field of environmental modeling.
    He is also a PhD candidate at the GIScience group, Department of Geography at University of Jena where he acts as a researcher in the environmental modeling field.
    At cynkra GmbH, Patrick is an R consultant with many years of experience in the following fields: CI/CD, package development, DevOps tasks, machine learning and spatio-temporal data handling.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{Jannes Muenchow}
	Biography text here.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{Eugenia Iturritxa}
	Biography text here.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{José Cortés}
	Biography text here.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{Bernd Bischl}
	Biography text here.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{Alexander Brenning}
	Biography text here.
\end{IEEEbiography}

>>>>

% The photo area is 1 in wide and 1.25 in long. The IEEE recommends that author photo images should be of 220 dpi (dots per inch) resolution and in gray scale with 8 bits/sample.
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./jpg/pschratz.jpeg}}]{Patrick Schratz}
%	[]{Patrick Schratz}
	is a Data Scientist working in Zurich, CH.
    His area of expertise is applied machine learning, more specifically the field of environmental modeling.
    He is a PhD candidate at the GIScience group, Department of Geography at University of Jena where he acts as a researcher in the environmental modeling field.
    At cynkra GmbH in Zurich, Patrick is an R consultant with many years of experience in the following fields: CI/CD, package development, DevOps tasks, machine learning and spatio-temporal data handling.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{Jannes Muenchow}
	Biography text here.
\end{IEEEbiography}
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./jpg/eiturritxa.jpg}}]{Eugenia Iturritxa}
	received the Ecology and Ph.D degree in Plant Protection from the Basque country University in 2001.
	Since 1999 her main research has focused on forest health, on the study of diverse species of native and introduced pathogenic fungi in forests and forest plantations.
	Her research includes the distribution of diseases, analysis of predisposing factors for them, genetic and phenotypic studies of populations and their epidemiology.
\end{IEEEbiography}
\begin{IEEEbiography}
	[]{José Cortés}
	received his B.S. in Mathematics and M.S. in Statistics from Arizona State University, Arizona, USA, in 2014 and 2016, respectively.
	Currently he is a PhD student at Friedrich-Schiller-University, Jena, Germany.
	He is a member of the International Max Planck Research School on Global Biogeochemical Cycles (IMPRS-gBGC, a joint program with the Max Planck Institute for Biogeochemistry.
	His research focuses on spatio-temporal trend detection in environmental data.
\end{IEEEbiography}
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./jpg/bbischl.jpg}}]{Bernd Bischl}
	obtained his Ph.D from Dortmund Technical University in 2013.
	He is a professor for "Statistical Learning and Data Science" at the Department of Statistics at the Ludwig-Maximilians-University Munich and a director of the "Munich Center for Machine Learning".
	His research interests include AutoML, model selection, interpretable ML and XAI.
\end{IEEEbiography}
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./jpg/abrenning.jpg}}]{Alexander Brenning}
	(Ph.D. 2005) graduated in mathematics at Technical University of Freiberg, Germany, and received his Ph.D. in geography from Humboldt-Universität zu Berlin.
	He served as an assistant professor and tenured associate professor in geomatics at the University from 2007 until 2015, when he was appointed as a full professor in geographic information science at Friedrich Schiller University Jena, Germany.
	Dr. Brenning's research interests include statistical and machine-learning techniques for environmental modeling and remote sensing.
	He has also contributed to open-source geocomputation by developing R packages for spatial cross-validation and GIS coupling.
\end{IEEEbiography}
